The document title

### 2021-03-10 manuscript/manuscript.Rmd
Configure the creation of a docx for the manuscript

---
# title: "The document title"
output:
  bookdown::pdf_document2:
    toc: false
    includes:
      in_header: "preamble.tex"
    latex_engine: lualatex
bibliography: bibliography.bib
csl: nlm.csl
---

@@

\section*{Introduction}

@@

\section*{Methods}

\subsection*{Participants}

@@

\subsection*{Protocol}

@@

\subsection*{Data processing}

@@

\subsection*{Statistical analyses}

@@

Regression equations to predict pRGFR, pVGRF, pRLR and pVLR were developed by linear mixed models. Body mass (kg) was tested as a predictor in all models. In addition, in the pRGRF and pVGRF models, pRACC and peak vertical ACC (pVACC; \textit{g}), respectively, were tested as predictors, while in the pRLR and pVLR models, peak resultant ATR (pRATR; $g\phantom{ }\mathrm{\phantom{ }\cdot s^{-1}}$) and peak vertical ATR (pVATR; $g\phantom{ }\mathrm{\phantom{ }\cdot s^{-1}}$), respectively, were tested as predictors. All predictors were tested as fixed effects and were shown to be significant. Subject and speed were tested as random effects, and the inclusion of both has showed to improve the models. Final models were chosen according to -2 log-likelihood statistics [@Field2012]. Traditional coefficient of determination (R\textsuperscript{2}) was represented by conditional R\textsuperscript{2}, that estimates the variance explained by the whole model [@Nakagawa2013].

@@

\section*{Results}

@@

\section*{References}

@@

\section*{Supplemental Material}

\subsection*{Supplemental Figure S1}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS1.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Relationship between peak ground reaction force and acceleration magnitudes. Data from accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Linear trends for each body mass index category are also depicted. Abbreviations: pRACC, peak resultant acceleration; pRGRF, peak resultant ground reaction force; pVACC, peak vertical acceleration; pVGRF, peak vertical ground reaction force.

@@

\subsection*{Supplemental Figure S2}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS2.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Relationship between peak loading and acceleration rates. Data from accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Linear trends for each body mass index category are also depicted. Abbreviations: pRAR, peak resultant acceleration rate; pRLR, peak resultant loading rate; pVAR, peak vertical acceleration rate; pVLR, peak vertical loading rate.

@@

\subsection*{Supplemental Figure S3}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS3.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Bland-Altman plots showing agreement between actual and predicted pGRF for accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Continuous thick lines show bias (average of the differences between actual and predicted values) while dashed lines show the limits of agreement (bias \pm 1.96 standard deviation). Abbreviations: pGRF, peak ground reaction force; pRGRF, peak resultant ground reaction force; pVGRF, peak vertical ground reaction force.

\subsection*{Supplemental Figure S4}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS4.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Bland-Altman plots showing agreement between actual and predicted pLR for accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Continuous thick lines show bias (average of the differences between actual and predicted values) while dashed lines show the limits of agreement (bias \pm 1.96 standard deviation). Abbreviations: pLR, peak loading rate; pRLR, peak resultant loading rate; pVLR, peak vertical loading rate.

>>>>

---
# title: "The document title"
output:
  bookdown::pdf_document2:
    toc: false
    includes:
      in_header: "preamble.tex"
    latex_engine: lualatex
  word_document:
    reference_docx: style_reference.docx
always_allow_html: true
bibliography: bibliography.bib
csl: nlm.csl
---

@@

# Introduction {.unnumbered}

@@

# Methods {.unnumbered}

## Participants {.unnumbered}

@@

## Protocol {.unnumbered}

@@

## Data processing {.unnumbered}

@@

## Statistical analyses {.unnumbered}

@@

Regression equations to predict pRGFR, pVGRF, pRLR and pVLR were developed by linear mixed models. Body mass (kg) was tested as a predictor in all models. In addition, in the pRGRF and pVGRF models, pRACC and peak vertical ACC (pVACC; \textit{g}), respectively, were tested as predictors, while in the pRLR and pVLR models, peak resultant ATR (pRATR; $g\phantom{ }\mathrm{\phantom{ }\cdot s^{-1}}$) and peak vertical ATR (pVATR; $g\phantom{ }\mathrm{\phantom{ }\cdot s^{-1}}$), respectively, were tested as predictors. All predictors were tested as fixed effects and were shown to be significant. Subject and speed were tested as random effects, and the inclusion of both has showed to improve the models. Final models were chosen according to -2 log-likelihood statistics [@Field2012]. Traditional coefficient of determination ($\mathrm{R^2}$) was represented by conditional $\mathrm{R^2}$, that estimates the variance explained by the whole model [@Nakagawa2013].

@@

# Results {.unnumbered}

@@

# References {.unnumbered}

@@

# Supplemental Material {.unnumbered}

## Supplemental Figure S1 {.unnumbered}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS1.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Relationship between peak ground reaction force and acceleration magnitudes. Data from accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Linear trends for each body mass index category are also depicted. Abbreviations: pRACC, peak resultant acceleration; pRGRF, peak resultant ground reaction force; pVACC, peak vertical acceleration; pVGRF, peak vertical ground reaction force.

@@

## Supplemental Figure S2 {.unnumbered}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS2.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Relationship between peak loading and acceleration rates. Data from accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Linear trends for each body mass index category are also depicted. Abbreviations: pRAR, peak resultant acceleration rate; pRLR, peak resultant loading rate; pVAR, peak vertical acceleration rate; pVLR, peak vertical loading rate.

@@

## Supplemental Figure S3 {.unnumbered}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS3.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Bland-Altman plots showing agreement between actual and predicted pGRF for accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Continuous thick lines show bias (average of the differences between actual and predicted values) while dashed lines show the limits of agreement (bias \pm 1.96 standard deviation). Abbreviations: pGRF, peak ground reaction force; pRGRF, peak resultant ground reaction force; pVGRF, peak vertical ground reaction force.

## Supplemental Figure S4 {.unnumbered}
\begin{figure}[ht]
	\captionsetup{singlelinecheck = false, format = hang, justification = raggedright, font = footnotesize, labelsep = space}
	\centering
	\begin{measuredfigure}
		\includegraphics[width=\textwidth]{figS4.png}
	\end{measuredfigure}
\end{figure}
\footnotesize Bland-Altman plots showing agreement between actual and predicted pLR for accelerometers worn at ankle (Panels A and D), lower back (Panels B and E) and hip (Panels C and F), for both the resultant vector (Panels A to C) and its vertical component (Panels D to F). Continuous thick lines show bias (average of the differences between actual and predicted values) while dashed lines show the limits of agreement (bias \pm 1.96 standard deviation). Abbreviations: pLR, peak loading rate; pRLR, peak resultant loading rate; pVLR, peak vertical loading rate.
